From physical principles to ???

### 2016-05-10 2015CompleteDerivation/completeDerivation.tex
Review integration justification

\begin{prop}\label{discrete_state_metric}
	Let $U \subseteq \mathcal{S}$ a set of states fully identified by a set of $n$ independent discrete state variables $q^i$. Let $\Delta q^i = q^i(U)$ the range of possibilities of each variable. Then $\#(\Delta q^i)=\#(\Delta \hat{q}^i) \; \forall i$ and $\#(U)=\prod\limits_{i=1}^{n}\#(\Delta q^i)=\prod\limits_{i=1}^{n}\#(\Delta \hat{q}^i)=\#(\hat{U})$ where $\hat{U}=\mathcal{T}_{\Delta t}(U)$ and $\#$ denotes the cardinality of the given set.
\end{prop}

@@

We will call a classical system one that is infinitesimally reducible. That is: it is made of arbitrarily small parts, which we call particles, and the state of the whole system coincides with the sum of the states of the parts. Given the state space $\mathcal{S}$ for the infinitesimal parts, a composite state $\mathcal{c}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

The notion that the parts are infinitesimal requires the co-domain of $\rho$ to be continuous, as opposed to discrete. The state space $\mathcal{S}$, instead, can have a discrete topology. For example, for a system composed of different tanks connected by pipes, the state of the composite system could be the overall distribution of water among the tanks. The amount in each tank is continuous (as we assume the water to be infinitesimally divisible) yet there are only a finite number of tanks the water can be placed into. As it links two physically distinguishable objects, $\rho$ is a continuous function for reasons discussed before.

@@

\begin{justification}
We claim $\mathcal{C}$ is an abelian group. $\mathcal{C}$ is a decomposable homogeneous system. $\mathcal{C}$ is an abelian group  by \ref{reducible_state_space}.

@@

We claim $\mathcal{C}$ is isomorphic to a subspace of $C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. $\forall \mathcal{c} \in \mathcal{C} \exists ! \rho_{\mathcal{c}}:\mathcal{S} \rightarrow \mathbbm{R}$ returning the amount of material for each state $\mathcal{s} \in \mathcal{S}$. $\rho \in C(\mathcal{S})$ by \ref{continuous_map}. Let $\varrho : \mathcal{C} \rightarrow C(\mathcal{S})$ such that $\varrho(\mathcal{c}) \mapsto \rho_\mathcal{c}$. 
As the system is reducible, two distinct composite states must represent different distributions. $\forall \mathcal{c_1}, \mathcal{c_2} \in \mathcal{C}, \mathcal{c_1} \neq \mathcal{c_2} \implies \varrho(\mathcal{c_1}) \neq \varrho(\mathcal{c_1})$. $\varrho$ is injective. $\varrho$ is a bijection between $\mathcal{C}$ and $\varrho(\mathcal{C})$. Let $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$, then $\varrho(\mathcal{c})=\varrho(\mathcal{c}_1)+\varrho(\mathcal{c}_2)$ as the amount of material of the composition of two states is the sum of the individual amounts. Let $\mathcal{c}_1=\tau(a)\mathcal{c}_2$, then $\varrho(\mathcal{c}_1)=a \varrho(\mathcal{c}_2)$ as $\tau(a)$ increases the amount of material by the factor $a$. $\varrho$ is a homomorphism. $\mathcal{C}$ is isomorphic to $\varrho(\mathcal{C}) \subseteq C(\mathcal{S})$ as vector spaces.
\end{justification}

@@

The ability to associate finite amount of material with sets of states allows us to define finite regions of $\mathcal{S}$ and compare them. Consider a region of position and momentum in phase space. If we are able to spread a finite amount of material into a non-infinitesimal uniform distribution, then we know we have a finite region. And the density will give us an indication of how big the region is: if we double the region, the density will halve. In other words: because we are describing densities over $\mathcal{S}$, we are able to give a unique measure $\mu$ for the size of sets of $\mathcal{S}$, a metric $d\mu$ and our positive linear functionals become integrals: $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.

@@

\begin{defn}\label{integration}
	The state space $\mathcal{S}$ for the particles of a homogeneous classical material is endowed with a Borel measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$.
\end{defn}

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each open set $U \subseteq \mathcal{S}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of the distribution for each particle state is positive then the total amount of material is positive.

	We claim that $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$. Let $U \subseteq \mathcal{S}$ be the open set of particle states associated with an outcome. Let $\mathcal{c} \in \mathcal{S}$ a composite state. As physically we always work with finite quantities, the amount of material of $\mathcal{c}$ associated with the outcome $U$ must be finite. $|\Lambda_{U}(\mathcal{c})| < \infty$.

	We claim that $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2}$ $\forall $ open $U_1, U_2 \in \mathcal{S}$. Let $U_1, U_2 \in \mathcal{S}$ be the open sets of particles states associated with two outcomes. Suppose $U_1 \cap U_2 = 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2}$ as the material found in $U_1 \cup U_2$ must be either in $U_1$ or $U_2$. Suppose $U_1 \cap U_2 \neq 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2} - \Lambda_{U_1 \cap U_2}$ as the sum of the material associated with each outcome will double count the intersection.

	We claim that each $U \subseteq \mathcal{S}$ is endowed with a Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. $\mathcal{S}$ is locally compact as it is a manifold. At each point there exists a compact open a neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff space on which is defined a positive linear function $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous compactly supported real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$.

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $V \subseteq \mathcal{S}$ an open set. Let $U \subseteq V$ not necessarily open. As $\rho_{\mathcal{c}}$ is continuous, $\int_{U} \rho_{\mathcal{c}} d \mu_V = \int_{\mathrm{Int} U} \rho_{\mathcal{c}} d \mu_V$. We extend $\Lambda_U \equiv \Lambda_{\mathrm{Int}U}$ to all sets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{\mathrm{Int} V \backslash U} \rho_{\mathcal{c}} d \mu_{\mathrm{Int} V \backslash U} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique for each open set in the family of all functionals. As $\mathcal{S}$ is locally compact, we can find a cover of compact sets. $\Lambda_{\mathcal{S}}(\mathcal{c})$ will be the sum of contributions of the elements of the cover and their intersections. As $\Lambda_U$ is always finite, $\Lambda_{\mathcal{S}}$ is a finite sum of finite contributions. Therefore we have  $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq L^1_{ew}(\mathcal{S}, \mu)$. TODO: can we prove mathematically that we have to span the whole space to be closed under linear combinations? 
\end{justification}

>>>>

\begin{prop}\label{discrete_state_metric}
	Let $U \subseteq \mathcal{S}$ a set of states fully identified by a set of $n$ independent discrete state variables $q^i$. Let $\Delta q^i \equiv q^i(U)$ the range of possibilities of each variable. Then $\#(\Delta q^i)=\#(\Delta \hat{q}^i) \; \forall i$ and $\#(U)=\prod\limits_{i=1}^{n}\#(\Delta q^i)=\prod\limits_{i=1}^{n}\#(\Delta \hat{q}^i)=\#(\hat{U})$ where $\hat{U}=\mathcal{T}_{\Delta t}(U)$ and $\#$ denotes the cardinality of the given set.
\end{prop}

@@

We will call a classical system one that is infinitesimally reducible. That is: it is made of arbitrarily small parts, which we call particles, and the state of the whole system coincides with the sum of the states of the parts. Given the state space $\mathcal{S}$ for the infinitesimal parts, which we assume it to be a manifold consistently with \ref{continuous_state_space}, a composite state $\mathcal{c}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

The notion that the parts are infinitesimal requires the co-domain of $\rho$ to be a real number, as opposed to an integer. The state space $\mathcal{S}$, instead, can have a discrete topology. For example, for a system composed of different tanks connected by pipes, the state of the composite system could be the overall distribution of water among the tanks. The amount in each tank is continuous (as we assume the water to be infinitesimally divisible) yet there are only a finite number of tanks the water can be placed into. As it links two physically distinguishable objects, $\rho$ is a continuous function as discussed before.

@@

\begin{justification}
We claim $\mathcal{C}$ is an abelian group. $\mathcal{C}$ is the state space for a decomposable homogeneous system. $\mathcal{C}$ is an abelian group  by \ref{reducible_state_space}.

@@

We claim $\mathcal{C}$ is isomorphic to a subspace of $C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. $\forall \mathcal{c} \in \mathcal{C} \exists ! \rho_{\mathcal{c}}:\mathcal{S} \rightarrow \mathbbm{R}$ returning the amount of material for each state $\mathcal{s} \in \mathcal{S}$. $\rho_{\mathcal{c}} \in C(\mathcal{S})$ by \ref{continuous_map}. Let $\varrho : \mathcal{C} \rightarrow C(\mathcal{S})$ such that $\varrho(\mathcal{c}) \mapsto \rho_\mathcal{c}$. 
As the system is reducible, two distinct composite states must represent different distributions. $\forall \mathcal{c_1}, \mathcal{c_2} \in \mathcal{C}, \mathcal{c_1} \neq \mathcal{c_2} \implies \varrho(\mathcal{c_1}) \neq \varrho(\mathcal{c_1})$. $\varrho$ is injective. $\varrho$ is a bijection between $\mathcal{C}$ and $\varrho(\mathcal{C})$. Let $\mathcal{c}=\mathcal{c}_1+\mathcal{c}_2$, then $\varrho(\mathcal{c})=\varrho(\mathcal{c}_1)+\varrho(\mathcal{c}_2)$ as the amount of material of the composition of two states is the sum of the individual amounts. Let $\mathcal{c}_1=\tau(a)\mathcal{c}_2$, then $\varrho(\mathcal{c}_1)=a \varrho(\mathcal{c}_2)$ as $\tau(a)$ increases the amount of material by the factor $a$. $\varrho$ is a homomorphism. $\mathcal{C}$ is isomorphic to $\varrho(\mathcal{C}) \subseteq C(\mathcal{S})$ as vector spaces.
\end{justification}

@@

The ability to associate finite amount of material with sets of states allows us to define finite regions of $\mathcal{S}$ and compare them. Consider a region of position and momentum in phase space. If we are able to spread a finite amount of material into a non-infinitesimal uniform distribution, then we know we have a finite region. And the density will give us an indication of how big the region is: if we double the region, the density will halve. In other words: because we are describing densities over $\mathcal{S}$, we are able to give a unique measure $\mu$ for the size of sets of $\mathcal{S}$. From the measure we get a metric $d\mu$ and our positive linear functionals become integrals: $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$.

@@

\begin{defn}\label{integration}
	Let $\mathcal{S}$ be the state space for the particles of a homogeneous classical material. Let each state $\mathcal{s} \in \mathcal{S}$ be fully identified by a finite number of independent state variables. Then $\mathcal{S}$ is endowed with a Borel measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$.
\end{defn}

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each $U \subseteq \mathcal{S}$ for which $\Lambda_U = \Lambda_{\mathrm{int}(U)}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ be the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of the distribution for each particle state is positive then the total amount of material is positive. Let $U \subseteq \mathcal{S}$ not necessarily open. Define $\Lambda_U$ as $\Lambda_{\mathrm{int}(U)}$.

	We claim that $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$. Let $U \subseteq \mathcal{S}$ be an open set of particle states associated with an outcome. Let $\mathcal{c} \in \mathcal{S}$ a composite state. The amount of material of $\mathcal{c}$ associated with the outcome $U$ must be finite, as physically we always work with finite quantities. $|\Lambda_{U}(\mathcal{c})| < \infty$. Let $U \subseteq \mathcal{S}$ not necessarily open. The same argument applies to $\mathrm{int}(U)$.

	We claim that $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2}$ $\forall $ $U_1, U_2 \in \mathcal{S}$. Let $U_1, U_2 \in \mathcal{S}$ be open sets of particle states associated with two outcomes. Suppose $U_1 \cap U_2 = 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2}$ as the material found in $U_1 \cup U_2$ must be either in $U_1$ or $U_2$. Suppose $U_1 \cap U_2 \neq 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2} - \Lambda_{U_1 \cap U_2}$ as the sum of the material associated with each outcome will double count the intersection. Let $U_1, U_2 \in \mathcal{S}$ not necessarily open. The same argument applies to their interiors.

	We claim that at each $\mathcal{s} \in \mathcal{S}$ there exists a neighborhood $U \subseteq \mathcal{S}$ endowed with a Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. Each $\mathcal{s} \in \mathcal{S}$ is identified by a finite number of independent state variables. $\mathcal{S}$ is a manifold. $\mathcal{S}$ is locally compact. At each point there exists a compact neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff topological space on which is defined a positive linear functional $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. As $\rho_{\mathcal{c}}$ is continuous $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{\mathrm{int}(U)} \rho_{\mathcal{c}} d \mu_U$ which is consistent with $\Lambda_U = \Lambda_{\mathrm{int}(U)}$.

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $U \subseteq V \subseteq \mathcal{S}$ two compact subsets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V \backslash U} \rho_{\mathcal{c}} d \mu_{\overline{V \backslash U}} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique and does not depend on the choice of neighborhood. As $\mathcal{S}$ is locally compact, we can find a cover of compact sets. $\Lambda_{\mathcal{S}}(\mathcal{c})$ will be the sum of contributions of the elements of the cover and their intersections. As $\Lambda_U$ is always finite, $\Lambda_{\mathcal{S}}$ is a finite sum of finite contributions. Therefore we have  $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq L^1_{ew}(\mathcal{S}, \mu)$. $G \subseteq C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$. Let $\rho_\mathcal{c}$ be the distribution associated with the state $\mathcal{c}$. Let $\rho \in C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ be a continuous function everywhere integral. If $\rho_\mathcal{c} \neq \rho$ then $\exists U \in \mathcal{S} | \int_{U} \rho_\mathcal{c} d \mu \neq \int_{U} \rho d \mu$. There exist an outcome in $\mathcal{S}$ that can physically distinguish the two distributions. There must be a state $\mathcal{c}_1 \in \mathcal{C} \; | \; \varrho_(\mathcal{c}_1)=\rho$. $\varrho : \mathcal{C} \rightarrow C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ is surjective. $\varrho$ is an isomorphism between $\mathcal{C}$ and $C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ as vector spaces.
\end{justification}
